Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-14 csf-2017/paper.tex
put terminology section in comment

\section*{Terminology ?}

\emph{capability safe}: 
Our unary logical relation is a semantic \emph{definition}
of which values for the
pc / register-file / word are capability safe.

\emph{adversary}: It doesn't sound ``sexy'' to constantly say ``an untrusted
piece of code'' should we adopt the convention that adversary refers
to an unstrusted piece of code?

\emph{memory}  we don't make a distinction between memory and memory
segments in the text  (to do so properly, we would need to explain why
assumptions
are reasonable, given that a real machine has finite memory, but we
need infinite domain for malloc spec, etc.)

>>>>

% \section*{Terminology ?}

% \emph{capability safe}: 
% Our unary logical relation is a semantic \emph{definition}
% of which values for the
% pc / register-file / word are capability safe.

% \emph{adversary}: It doesn't sound ``sexy'' to constantly say ``an untrusted
% piece of code'' should we adopt the convention that adversary refers
% to an unstrusted piece of code?

% \emph{memory}  we don't make a distinction between memory and memory
% segments in the text  (to do so properly, we would need to explain why
% assumptions
% are reasonable, given that a real machine has finite memory, but we
% need infinite domain for malloc spec, etc.)
